Calls vs IMD

### 2021-11-01 output/calls_vs_imd.Rmd
updated IMD stuff

@@

@@

total_calls <- cheshire_calls %>% group_by(lsoa) %>% count() %>% 
  left_join(., imd, by = c("lsoa" =  "lsoa_name_2011"))

@@

ggplot(total_calls %>% filter(!is.na(index_of_multiple_deprivation_imd_decile)), aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n )) + 
  geom_boxplot() + 
  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = 50000, label = paste0("n = ",n))) + 
  scale_y_log10() + 
  labs(title = "Total calls from LSOAs in each IMD decile 2015-2020") + 
  xlab("IMD decile (1 = most and 10 = least deprived)") + 
  ylab("Number of calls (all types)") + 
  theme_bw()

@@

```{r Admin}
plot_imd("Advice/Directions/Admin")
```

@@

```{r Alarms}
plot_imd("alarms")
```

@@

```{r Wildlife}
plot_imd("animals")
```

@@

```{r ASB}
plot_imd("ASB")
```

@@

```{r Burglary - Commercial}
plot_imd("Burglary - Business/Commercial")
```

@@

```{r Burglary - Residential}
plot_imd("Burglary - Residential")
```

@@

plot_imd("Civil Disputes")
```

@@

plot_imd("Code Zero")
```

@@

plot_imd("Collapse/Illness/Injury/Trapped")
```

@@

plot_imd("Complaints Against Police")
```

@@

```{r Concern For Safety}
plot_imd("Concern For Safety")
```

@@

```{r Criminal Damage}
plot_imd("Criminal Damage")
```

@@

```{r Domestic Incident}
plot_imd("Domestic Incident")
```

@@

```{r Drug Related Offences}
plot_imd("Drugs")
```

@@

```{r Firearms}
plot_imd("firearms")
```

@@

```{r Fraud}
plot_imd("Fraud")
```

@@

```{r Hate Incident}
plot_imd("Hate Incident")
```

@@

```{r Highway Disruption}
plot_imd("Highway Disruption")
```

@@

```{r Missing Person}
plot_imd("Missing Person")
```

@@

```{r Other -Admin Calls}
plot_imd("other - admin")
```

@@

```{r Other - minor}
plot_imd("other - minor")
```

@@

```{r Police Generated}
plot_imd("Police Generated")
```

@@

```{r Breach of Peace}
plot_imd("Prevent Potential Breach of the Peace")
```

@@

```{r Property Lost/Found}
plot_imd("Property Lost/Found")
```

@@

```{r Road Related Traffic}
plot_imd("Road Related Traffic Offence")
```

@@

```{r Robbery}
plot_imd("Robbery")
```

@@

```{r Sexual Offences}
plot_imd("Sexual Offences")
```

@@

```{r Shoplifting}
plot_imd("Shoplifting")
```

@@

```{r Sudden Death}
plot_imd("Sudden Death")
```

@@

```{r Suspicious Activity}
plot_imd("Suspicious Activity")
```

@@

```{r Suspicious Package}
plot_imd("Suspicious Package")
```

@@

```{r Theft From Motor Vehicle}
plot_imd("Theft From Motor Vehicle")
```

@@

```{r Theft of Motor Vehicle}
plot_imd("Theft Of Motor Vehicle")
```

@@

```{r Theft Other}
plot_imd("Theft Other")
```

@@

```{r Traffic Collisions}
plot_imd("traffic collision")
```

@@

```{r Violence/Harassment}
plot_imd("Violence/Harassment")
```

@@

```{r Warrant/Bail}
plot_imd("warrant/bail issue")
```

>>>>

lsoa_filler <- bind_rows(data.frame(lsoa = unique(cheshire_imds$LSOA11NM),
                          pre_post = "Pre-COVID"), 
                         data.frame(lsoa = unique(cheshire_imds$LSOA11NM),
                          pre_post = "Post-COVID"))

@@

plot_imd_prepost <- function(inc_type) {

  pre_calls <- cheshire_calls %>% 
    filter(incident_type_new == inc_type) %>% 
  mutate(pre_post = ifelse(incident_date_time < dmy("31/01/2020"), "Pre-COVID", "Post-COVID")) %>%   group_by(lsoa, pre_post) %>% count() %>% 
  left_join(lsoa_filler, .) %>%
    mutate(n = replace_na(n, 0)) %>% 
    left_join(., cheshire_imds, by = c("lsoa" = "LSOA11NM")) %>% 
  filter(!is.na(index_of_multiple_deprivation_imd_decile)) %>%  # check why NAs
  mutate(n = replace_na(n, 0), 
         n_per_yr = ifelse(pre_post == "Pre-COVID", n/5,n))

labs_df <- pre_calls %>% 
  group_by(index_of_multiple_deprivation_imd_decile) %>% summarise(n = n_distinct(lsoa))

 p <-  ggplot() + 
  geom_boxplot(data = pre_calls, aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n_per_yr, color = pre_post)) + 
  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = max(pre_calls$n_per_yr, na.rm = TRUE) + 10, label = paste0("n = ",n))) +
  labs(title = "Total calls from LSOAs in each IMD decile pre and post COVID") + 
  xlab("IMD decile (1 = most and 10 = least deprived)") + 
  ylab(paste0("Number of ",inc_type," calls (per year)")) + 
       scale_y_log10() + 
  theme_bw() + 
  theme(legend.position = c(0.87, 0.75))
 return(p)

@@

total_calls <- cheshire_calls %>% group_by(lsoa) %>% count() %>% 
  left_join(., imd, by = c("lsoa" =  "lsoa_name_2011")) %>%
  filter(!is.na(index_of_multiple_deprivation_imd_decile))  # check why NAs

@@

ggplot(total_calls , aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n )) + 
  geom_boxplot() + 
  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = 50000, label = paste0("n = ",n))) + 
  scale_y_log10() + 
  labs(title = "Total calls from LSOAs in each IMD decile 2015-2020") + 
  xlab("IMD decile (1 = most and 10 = least deprived)") + 
  ylab("Number of calls (all types)") + 
  theme_bw()

```{r prepostcovidbox}

pre_calls <- cheshire_calls %>% 
  mutate(pre_post = ifelse(incident_date_time < dmy("31/01/2020"), "Pre-COVID", "Post-COVID")) %>%   group_by(lsoa, pre_post) %>% count() %>% 
  left_join(lsoa_filler, .) %>%
    mutate(n = replace_na(n, 0)) %>% 
  left_join(., cheshire_imds, by = c( "lsoa" = "LSOA11NM")) %>%
  filter(!is.na(index_of_multiple_deprivation_imd_decile)) %>%  # check why NAs
  mutate(n = replace_na(n, 0), 
         n_per_yr = ifelse(pre_post == "Pre-COVID", n/5,n))

labs_df <- pre_calls %>% group_by(pre_post, index_of_multiple_deprivation_imd_decile) %>% count()

ggplot(pre_calls, aes(x = as.factor(index_of_multiple_deprivation_imd_decile), y = n_per_yr, color = pre_post)) + 
  geom_boxplot() + 
  geom_label(data = labs_df, aes(x = index_of_multiple_deprivation_imd_decile, y = max(pre_calls$n_per_yr + 100), label = paste0("n = ",n))) +
  labs(title = "Total calls from LSOAs in each IMD decile pre and post COVID") + 
  xlab("IMD decile (1 = most and 10 = least deprived)") + 
  ylab("Number of calls (per year)") + 
  theme_bw() + 
  theme(legend.position = c(0.87, 0.75))

@@

```{r Admin}
plot_imd("Advice/Directions/Admin")
plot_imd_prepost("Advice/Directions/Admin")

@@

```{r Alarms}
plot_imd("alarms")
plot_imd_prepost("alarms")

@@

```{r Wildlife}
plot_imd("animals")
plot_imd_prepost("animals")
```

@@

```{r ASB}
plot_imd("ASB")
plot_imd_prepost("ASB")
```

@@

```{r Burglary - Commercial}
plot_imd("Burglary - Business/Commercial")
plot_imd_prepost("Burglary - Business/Commercial")
```

@@

```{r Burglary - Residential}
plot_imd("Burglary - Residential")
plot_imd_prepost("Burglary - Residential")
```

@@

plot_imd("Civil Disputes")
plot_imd_prepost("Civil Disputes")
```

@@

plot_imd("Code Zero")
plot_imd_prepost("Code Zero")
```

@@

plot_imd("Collapse/Illness/Injury/Trapped")
plot_imd_prepost("Collapse/Illness/Injury/Trapped")
```

@@

plot_imd("Complaints Against Police")
plot_imd_prepost("Complaints Against Police")
```

@@

```{r Concern For Safety}
plot_imd("Concern For Safety")
plot_imd_prepost("Concern For Safety")
```

@@

```{r Criminal Damage}
plot_imd("Criminal Damage")
plot_imd_prepost("Criminal Damage")
```

@@

```{r Domestic Incident}
plot_imd("Domestic Incident")
plot_imd_prepost("Domestic Incident")
```

@@

```{r Drug Related Offences}
plot_imd("Drugs")
plot_imd_prepost("Drugs")
```

@@

```{r Firearms}
plot_imd("firearms")
plot_imd_prepost("firearms")
```

@@

```{r Fraud}
plot_imd("Fraud")
plot_imd_prepost("Fraud")
```

@@

```{r Hate Incident}
plot_imd("Hate Incident")
plot_imd_prepost("Hate Incident")
```

@@

```{r Highway Disruption}
plot_imd("Highway Disruption")
plot_imd_prepost("Highway Disruption")
```

@@

```{r Missing Person}
plot_imd("Missing Person")
plot_imd_prepost("Missing Person")
```

@@

```{r Other -Admin Calls}
plot_imd("other - admin")
plot_imd_prepost("other - admin")
```

@@

```{r Other - minor}
plot_imd("other - minor")
plot_imd_prepost("other - minor")
```

@@

```{r Police Generated}
plot_imd("Police Generated")
plot_imd_prepost("Police Generated")
```

@@

```{r Breach of Peace}
plot_imd("Prevent Potential Breach of the Peace")
plot_imd_prepost("Prevent Potential Breach of the Peace")
```

@@

```{r Property Lost/Found}
plot_imd("Property Lost/Found")
plot_imd_prepost("Property Lost/Found")
```

@@

```{r Road Related Traffic}
plot_imd("Road Related Traffic Offence")
plot_imd_prepost("Road Related Traffic Offence")
```

@@

```{r Robbery}
plot_imd("Robbery")
plot_imd_prepost("Robbery")
```

@@

```{r Sexual Offences}
plot_imd("Sexual Offences")
plot_imd_prepost("Sexual Offences")
```

@@

```{r Shoplifting}
plot_imd("Shoplifting")
plot_imd_prepost("Shoplifting")
```

@@

```{r Sudden Death}
plot_imd("Sudden Death")
plot_imd_prepost("Sudden Death")
```

@@

```{r Suspicious Activity}
plot_imd("Suspicious Activity")
plot_imd_prepost("Suspicious Activity")

@@

```{r Suspicious Package}
plot_imd("Suspicious Package")
plot_imd_prepost("Suspicious Package")

@@

```{r Theft From Motor Vehicle}
plot_imd("Theft From Motor Vehicle")
plot_imd_prepost("Theft From Motor Vehicle")

@@

```{r Theft of Motor Vehicle}
plot_imd("Theft Of Motor Vehicle")
plot_imd_prepost("Theft Of Motor Vehicle")

@@

```{r Theft Other}
plot_imd("Theft Other")
  plot_imd_prepost("Theft Other")

@@

```{r Traffic Collisions}
plot_imd("traffic collision")
plot_imd_prepost("traffic collision")

@@

```{r Violence/Harassment}
plot_imd("Violence/Harassment")
plot_imd_prepost("Violence/Harassment")

@@

```{r Warrant/Bail}
plot_imd("warrant/bail issue")
plot_imd_prepost("warrant/bail issue")
```
